---
title: "Lab 00 - Hello IDS!"
author: "Max Creed"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("benji", "max", "jamie", 
           "gregor", "tom", "cameron"),
  github_username = c("tomdsimpson", "benjiedmondson", "jd43", 
                      "gregor-mackay", "cameron", "maxx-creed"), 
  colour = c("thistle3", "cadetblue3", "darkgreen", 
             "steelblue", "navyblue", "salmon"),
  hobby = c("guitar", "cycling", "writing", 
            "baking", "drawing", "sports"),
  favourite_number = c(2, 3, 7, 4, 7, 8)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


A bar graph of the team's favourite number.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Username", 
          y = "Favourite number",
          title = "Favourite number of teammates")
```

Change the names of the titles, subtitles etc.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

There is no difference in the amount of people with the hobbies, so it doesn't display them well. A table would display it better.
